---
title: "KEVIN W. GILDS, MPA"
subtitle: "Expertise in Collecting, Managing, and Analyzing Data"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

```{r echo=FALSE, messages=FALSE, warning=FALSE}
library(knitr)
library(timevis)
```


Cell: 863-399-4363  | email: kevingilds@gmail.com  | Lakeland, FL 
------------- | -------------                      |--------------
      

### Skill Summary

Excel/Access|Calculate/Interpret Statistics|R Programming | Git/Github | SQL
-----------| ---|--------------|-----------|--------------|------------|

### Work Experience


DATA SCIENCE


* **Created functions, scripts and reports in R to manage survey and academic data for the Get REAL! statewide mentoring program:** resulting in a work process that is automated and reproducible.

* **Developed Shiny dashboard application to communicate data entry status from multiple site locations** resulting in keeping client updated on data entry progress. 


* **Developed best practices to sanitize data and merge spreadsheets using the Vlookup Function:** Resulting in increased efficiency in meeting performance measures and helping consumers get services faster.

* **Identified data sources and requirements to automate billing process and colloaborated with MIS to implement**: resulting in saving 20 hours of data entry and improving efficiency of billing process.     


* **Developed Google Drive Form/Spreadsheet combination to process 800+ referrals a month:** resulting in increasing data quality,  real time reporting of workload, and faster response time to referrals.
   



PROJECT MANAGMENT

* **Manage program databases and identify needed data to make more effective reports and queries:** resulting in automated reports for management and partners.

* **Led team in managing the process of helping seniors obtain eligibility for Long Term Care Services:** assigned workloads, set milestones, and monitored progress of monthly releases, resulting in achieving performance measures every month over 2 years.

* **Monitored phone calls and staff documentation to ensure quality assurance standards were being met:** resulting in the identification of training needs for staff to help improve communication to consumers.

* **Generate staff productivity reports that measursed staff productivity:** resulting in conversations with teams members about their weekly productivity and providing technical assistance to remove barriers to success.

* **Created videos and written documentation to teach and document technical processes to manage data and workflow:** resulting in delegations of tasks and staff development.


SHINY APPLICATIONS

[Florida School Absences](https://tidydatabykwg57.shinyapps.io/flabsences/)



# Work History

```{r echo=FALSE}
data <- data.frame(
  id      = 1:6,
  content = c("Senior Connection Center"  , "Evaluation Consultant"  ,"Girl Scouts of WCF", "Career Source Pinellas", "Cby25 Initiative", "Camelot Community Care"),
  start   = c("2013-07-13", "2013-09-01", "2011-07-08", "2011-01-10","2010-01-08", "2007-04-07" ),
  end     = c(NA,NA, NA, NA, NA, NA)
)

timevis(data,width=1000, showZoom=FALSE)
```


```{r echo=FALSE,eval=FALSE}
employement <- data.frame(
  
  employer = c("Senior Connection Center", "Consultant"  ,"Girl Scouts of WCF", "Career Source Pinellas", "Cby25 Initiative", "Camelot Community Care"),
  job_title =c("Veterans Services Contract Coordinator", "Interm Veteran Services Contract Coordinator", "Long Term Care services Coordinaotr",  "Quality Assurance Coordinator", "Special Projects Coordinator", "Quality Assurance and Data Specialist", "Quality Assurance and Data Specialist"),
  start   = c("01-2017", "11-2016", "09-2013", "07-2013", "07-2011", "01-2011", "01-2010", "04-2010" ),
  end     = c("Present","11-2016", "Present", "04-2013", "07-11", "11-2010")
)
```


```{r echo=FALSE, eval=FALSE }

test_employ <- data.frame(
	


id = 1:4,

start   = c(
	"2013-07-13", 
	"2013-09-01", 
	"2011-07-08", 
	"2011-01-10"
),
  
	end     = c(
		NA,
		NA, 
		NA, 
		NA
		),
  

content = c(
    ("Senior Connection Center", "Veteran Services Contract Coordinator", "Interm Veteran Services Contract Coordinator"),
    ("Consultant", "Girl Scouts of West Central Florida--Get REAL Program"),
   ("Girl Scouts WCF", "Quality Assurance Coordinator"),
    ("Career Source Pinellas", "Special Projects Coordinator")
    
  )
)

timevis(test_employ,width=1000, showZoom=FALSE)
```


