---
type: "itemized"
title: "Mapped School District Absences"
subtitle: Average percent by School District
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(httr)
library(ggmap)
library(DT)
```

I came across this data set from the Florida Department of Education in March. In Florida school districts are organized by county and I saw this as an opportunity to improve my mapping skills.

This [tutorial](http://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html) from Erin C. Anderson  was instrumental in being able to complete this project. In fact a lot of the code chunks were stolen. 

## Data

The [Florida Department of Education](http://www.fldoe.org/accountability/data-sys/edu-info-accountability-services/pk-12-public-school-data-pubs-reports/students.stml) provides data on their website regarding the number of students by school that have missed more than 21 days of school. [Go here for more information on this data](https://tidydatabykwg57.shinyapps.io/flabsences/)

```{r echo=FALSE, message=FALSE, comments=FALSE}
url <- 'http://www.fldoe.org/core/fileparse.php/7584/urlt/1516ABS21DAYSchool.xls' #location of data on the internet


httr::GET(url, write_disk(absences <- tempfile(fileext = ".xls"))) #obtain the spreadsheet file from the internet

absences_2 <- readxl::read_excel(absences, skip =2) #read the spreadsheet file and skip the first two rows

absences_2 <- janitor::clean_names(absences_2) #Change column names with the Janitor.


absences_2 <- dplyr::rename(absences_2, "absent_21_plus" = "absent_21_days_or_over") #Change name again to shorten 

absences_2 <- dplyr::select(absences_2, 2, 4:6) #select columsn of interest

absences_2$enrollments <- as.numeric(absences_2$enrollments) #Change data to numeric format
absences_2$absent_21_plus <- as.numeric(absences_2$absent_21_plus) #change data to numeric format

absences_2 <- dplyr::mutate(absences_2, percent = absent_21_plus / enrollments) 

#calculate percent 
absences_2 <- dplyr::mutate(absences_2, percent = percent *100) #Convert from decimal 





```



I want to map the average percent of students who missed 21 or more days during the 2015-2016 school year. Below is a tibble of the output. 
```{r echo=FALSE}
absent_21 <- absences_2 %>%
  group_by(district_name) %>%
  summarise(mean = mean(percent, na.rm = TRUE)) 
  


absent_21$mean <- round(absent_21$mean, 2)

absent_21
```


## Working with ggmap


The first step is extract data to build the map. 

```{r echo=TRUE, message=FALSE}
#get state map
states <- map_data("state")

```

This code gets the parameters for Florida

```{r echo=TRUE}
fl_df <- subset(states, region == "florida")

```

The next step is to extract county parameters from Florida

```{r echo=TRUE, eval=TRUE}
counties <- map_data("county")
fl_county <- subset(counties, region == "florida")

```


This chunk of code will display the state of Florida. 
```{r echo=TRUE, warning=FALSE}
fl_base <- ggplot(data = fl_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_fixed(1.3) + 
  geom_polygon(color = "black", fill = "gray")
fl_base + theme_nothing()

```


This code chunk overlays the county shapes onto the Florida Map. 
```{r echo=TRUE, warning=FALSE}
fl_base + theme_nothing() + 
  geom_polygon(data = fl_county, fill = NA, color = "white") +
  geom_polygon(color = "black", fill = NA)  # get the state border back on top
```





## More data munging


In this chunk, I changed the name of the variable district_name to match the county data set. Case matters and the school district data set needed to be made lower in preparation of joining the data sets.  


```{r echo=TRUE}
absent_21_c <- absent_21 %>%
  rename("subregion" = "district_name")

absent_21_c$subregion <- tolower(absent_21_c$subregion)




```

Not all of the district_name and map data perfectly match. This is code will fix that. You will see that the anti-join function is an easy way to test. 

```{r echo=TRUE}

absent_21_c$subregion <- gsub("dade", "miami-dade", fixed = TRUE, absent_21_c$subregion)

absent_21_c$subregion <- gsub("desoto", "de soto", fixed = TRUE, absent_21_c$subregion)

absent_21_c$subregion <- gsub("st. johns", "st johns", fixed = TRUE, absent_21_c$subregion)

absent_21_c$subregion <- gsub("st. lucie", "st lucie", fixed = TRUE, absent_21_c$subregion)




```



## Ready to Join

This code chunk joins the two data sets. 


```{r }

map_d <- inner_join(fl_county, absent_21_c, by = "subregion")



```

This code chunk uses the anti-join function to ensure that all the counties and school district names match up. 

```{r}

non_match <- anti_join(fl_county, absent_21_c, by = "subregion")

non_match


```

This code chunk sets parameters for the map outline. 

```{r  }
ditch_the_axes <- theme(
  axis.text = element_blank(),
  axis.line = element_blank(),
  axis.ticks = element_blank(),
  panel.border = element_blank(),
  panel.grid = element_blank(),
  axis.title = element_blank()
  )



```


This code chunk plots the data from the school districts on to the map. 

```{r}

map_fl_school_absences <- fl_base + 
      geom_polygon(data = map_d, aes(fill = mean), color = "white") +
      geom_polygon(color = "black", fill = NA) +
      theme_bw() +
      ditch_the_axes

map_fl_school_absences

```

Similar to the example in the tutorial; the difference between school districts is not easily distinguishable on the map. This code chunk below  is an example of how to add more  color to the map. 

```{r }
eb2 <- map_fl_school_absences + 
    scale_fill_gradientn(colours = rev(rainbow(7)),
                         breaks = c(2, 4, 10, 100, 1000, 10000),
                         trans = "log10")
eb2
```


