---
title: 'Test Driving readxl'
author: Kevin
date: '2018-02-23'
slug: test-driving
categories: []
tags: []
---

# Introduction

I am interested in school attendance data and found an interesting data set on the Florida Department of Education Website. This seemed like a good time to learn the ` r readxl package ` in order to wrangle spreadsheets in the wild. This post closely follows closely with theexamples on the [Github Repo](https://github.com/tidyverse/readxl). 

The file consists of data from a survey of schools in Florida that provides a count of students who were absent more than 21 days in the school year 2015-2016. 

```{r load_libraries}
library(tidyverse)
library(readxl)
library(httr)
library(knitr)
```

### Getting the data

The url of the data set is below
```{r url}
url <- 'http://www.fldoe.org/core/fileparse.php/7584/urlt/1516ABS21DAYSchool.xls'

```

Use the Get function from httr to grab the file
```{r get file}
GET(url, write_disk(absences <- tempfile(fileext = ".xls")))

```



### Read the data
```{r}
absences_1 <- read_excel(absences)

```

### Check the data out with the str function
```{r}
str(absences_1)
```


### Display the data
```{r}
absences_1
```

The output is not in a tidy format. The first row has a title and the second row provides a description of the data. Lets extract just the meta data using ` r (n_max = 2)`.  

```{r meta}
meta <- read_excel(absences, n_max = 2)

meta
```

This is not exactly what I want. Using ` r (n_max = 2)` we captured the title and message about the data but we also captured the other columns and row information.  I am going to use the range argument to isolate the title and description of the data. 

```{r meta_1}
meta_1 <- read_excel(absences, range="A1:A2")

meta_1
```

An important warning about the data is cut off in the blog down output. I am going to isolate on the cell to clearly display the message about the data. 

```{r meta_2}
meta_2 <- read_excel(absences, range="A2")

meta_2

```

This did the trick. The message indicates that an asterisk is used when there is less than 10 students at a school. There is a ` r (na)` argument in the read_excel function but I could not get it work with a plain asterisk or an asterisk in quotes. Maybe a regular expression would work. 

```{r eval=FALSE}
absences_2 <- read_excel(absences, skip =2, na = "*")

absences_2 <- read_excel(absences, skip =2, na = *)


```


### Let me introduce you to skip:

Now, that we have the title and message about the data, let us put the data in tidy format. From our exercise above we know that the first two rows are not helpful. Fortunately we can use the ` r (skip = 2)` argument to bypass the first 2 rows. 

```{r}
absences_2 <- read_excel(absences, skip = 2)


```

### Use str again to check what we are dealing with
```{r}
str(absences_2)
```

Lovely, we are going to have to convert some of these variables to numeric. 

```{r}

absences_2$Enrollments <- as.numeric(absences_2$Enrollments)

absences_2$`Absent 21 Days or Over` <- as.numeric(absences_2$`Absent 21 Days or Over`)

absences_2$`% Absent 21 or More Days` <- as.numeric(absences_2$`% Absent 21 or More Days`)

```

```{r}
str(absences_2)
```

In part II, we will dive into the data. Stay tuned. 

